---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# m.shortcuts

<!-- badges: start -->
`r badger::badge_devel("AngelCampos/m.shortcuts", "blue")`
<!-- badges: end -->

## Description 

R package with sourced, original, and wrappers to recurrent functions I like 
and find recurrently useful.

## Installation

You can install the development version from
[GitHub](https://github.com/AngelCampos/m.shortcuts) typing in the following 
commands in the R console:

```{r, installation, eval = F}
if (!requireNamespace("remotes", quietly = TRUE))
    install.packages("remotes")
devtools::install_github("AngelCampos/m.shortcuts", build_vignettes = TRUE)
```

## Functions list

- check_figs(): Make a table of figures in 'figs' dir, generated in .R scripts 
and plot in .Rmd scripts
- ggBoxplot(): Shortcut for a ggplot2 boxplot
- intervalHeatmap(): Heatmap over 3 dimensions. It divides a vector over a 
set number of intervals over two dimensions. Useful to understand how values
distribute across 2 dimensions.
- lsos(): Improved list of objects. List the ten biggest objects in the global 
environment by default.
- multiplot(): An alternative to plot several plots, but it does not work to 
save to file.
- rmTmp(): Remove all objects in the global environment that start with 'tmp'.
